|

### 2021-03-23 97-Discussion.Rmd
Updates

@@

* The management of

Doing systematic reviews as a

@@

Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the)

@@

>>>>

## Triangulation

Summary table of different studies and results

## Discussion of E-values

How strong unmeasured confounding would have to be in order to explain the observed effect.

Heavily criticised in a range of papers.

## Use of concensus panel to bring everything together

@@

* That systematic review should no be

@@

Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).

@@

P

### 2021-03-23 front-and-back-matter/99-appendices.Rmd
Updates

## Chapter 1 {#appendix-chapter-1}

## Chapter 2 {#appendix-chapter-2}

>>>>

## Chapter \@ref(intro-heading) {#appendix-into}

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}

### Search strategy {#appendix-search-strategy}

### Code to search preprints {#appendix-medrxivr-code}

<!-- Double check this is the final code used -->

library(medrxivr)

mx_data <- mx_api_content(to_date = "2019-09-01")

bx_data <- mx_api_content(server = "biorxiv",
                                    to_date = "2019-09-01")

topic1 <- c("statin",
            mx_caps("ldl"),
            mx_caps("hdl"),
            mx_caps("TG"),
            paste0("\\b",mx_caps("TC"),"\\b"),
            "ezetim",
            "lipoprotein",
            "lipid",
            "cholesterol")

topic2 <- c(mx_caps("dementia"),
            mx_caps("alzheim"),
            mx_caps("MCI"),
            mx_caps("mild cognitive"))

query <- list(
  topic1,
  topic2
)

test <- mx_search(bx_data, query)

test2 <- mx_search(mx_data, query)

### MR risk of bias tool {#appendix-mr-rob}

## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
